---
title: 'Scouting Report Template'
author: "Birch Herring-Jackson,Dante Maurice,Lance Brady"
date: "06/18/2024"
---

```{r setup-global, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = FALSE, echo = FALSE)
```

### Load in Libraries
```{r load-libraries, include=FALSE}
library(tidyverse)
library(reshape2)
library(tidyr)
library(dplyr)
library(lubridate)
library(kableExtra)
library(readxl)
library(ggplot2)
library(gt)
library(writexl)
library(zip)
library(readr)
library(rvest)
library(xml2)
```


## Load All Data from Relievers
```{r}

unzip("New England.zip", exdir = "unzipped_files")
file_list <- list.files(path = "unzipped_files", pattern = "*.csv", full.names = TRUE)

# Read and combine all CSV files
data_list <- lapply(file_list, read.csv)  # read.csv() reads the header by default
data_list <- lapply(data_list, function(df) {
  df$CatcherId <- as.character(df$CatcherId)
  return(df)})
combined_data <- bind_rows(data_list)

# Write the combined data to a new Excel file
write_xlsx(combined_data, "Knockouts.xlsx")
#This creates an entire team's data sheet, hitters and all, which will make other projects easier down the road.
```

```{r}
TEAM=read_excel("Knockouts.xlsx")
pitcher=TEAM %>% filter(Pitcher %in% c("Sam Ryan"))
pitcher=pitcher %>% drop_na(TaggedPitchType) %>% drop_na(RelSpeed)%>% drop_na(SpinRate) %>% drop_na(HorzApprAngle) %>% drop_na(VertApprAngle)
pitcher$ID <- seq.int(nrow(pitcher))
```

Colors!
```{r, include=FALSE}
## Define Universal Pitch Colors
pitch_colors <- c(
  "Fastball" = "blue",
  "Slider" = "orange",
  "Changeup" = "darkgreen",
  "2-Seam Fastball" = "red",
  "Curveball" = "purple",
  "Cutter" = "brown",
  "Splitter" = "pink",
  "Knuckleball" = "grey",
  "Slurve" = "purple"
)
```

Scrapes Baseball Reference to give us Season Performance
```{r}

url <- "https://www.baseball-reference.com/register/player.fcgi?id=ryan--002sam"  


webpage <- read_html(url)


stats_table <- webpage %>%
  html_node("table#standard_pitching") %>%  
  html_table()


stats_df <- as.data.frame(stats_table)



season_stats=stats_df %>% filter(Year==2024)
season_stats=season_stats %>% select(Year, Tm, G, IP, ERA, R, ER, H, SO, BB, SO9, BB9, WHIP, HR)

season_stats$WHIP <- as.numeric(as.character(season_stats$WHIP))

# Creating a gt table from the dataframe
br_table <- season_stats %>%
  gt() %>%
  tab_header(title = "2024 Season Stats") %>%
  cols_label(
    Year= "Year",
    Tm="Team",
    G = "G",
    IP = "IP",
    ERA = "ERA",
    R = "R",
    ER = "ER",
    H = "H",
    SO = "K",
    BB = "BB",
    SO9= "K/9",
    BB9= "BB/9",
    WHIP = "WHIP",
    HR = "HRA"
  ) %>%
  fmt_number(
    columns = vars(IP, ERA, BB9, SO9, WHIP),
    decimals = 2
  ) %>%
  fmt_integer(
    columns = vars(Year, G, R, ER, H, SO, BB, HR)
  ) %>%
  tab_style(
    style = cell_fill(color = "lightgrey"),
    locations = cells_column_labels()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels()
  ) %>%
  tab_options(
    table.border.top.color = "black",
    table.border.bottom.color = "black",
    table.border.top.width = px(3),
    table.border.bottom.width = px(3)
  ) %>%
  tab_style(
    style = list(
      cell_borders(sides = "top", color = "black", weight = px(1)),
      cell_borders(sides = "bottom", color = "black", weight = px(1))
    ),
    locations = cells_body(columns = vars(Year, Tm, G, IP, ERA, R, ER, H, SO, BB, SO9, BB9, WHIP, HR))
  ) %>%
  cols_align(align = "center", columns = everything())
```

```{r}
br_table

```

Can be used before/after pitch cleaning to see progress
```{r}
pitcher %>%
  group_by(TaggedPitchType) %>%
  summarize(count = n()) %>% mutate(percentage = (count / sum(count)) * 100,)
```

Pitch Checking
```{r, include = FALSE}
## Tilt/Spin Check for Data Cleaning
pitch_checking=pitcher %>%
  group_by(TaggedPitchType) %>%
  select("ID", "Date", "RelSpeed","Tilt","yt_Efficiency", "TaggedPitchType", "RelSpeed", "SpinRate", "HorzBreak", "InducedVertBreak")
# I included date because it is good to see if a pitcher has improved 
# velocity or other metrics in his last start or two
```

Correct pitches as necesary (example code below)
```{r}
pitcher$TaggedPitchType[pitcher$TaggedPitchType == "Curveball"] = "Slurve" 
pitcher$TaggedPitchType[pitcher$TaggedPitchType == "Slider"] = "Slurve"
pitcher$TaggedPitchType[pitcher$TaggedPitchType == "Splitter"] = "Changeup"
pitcher$TaggedPitchType[pitcher$TaggedPitchType == "Sinker"] = "Fastball"
pitcher$TaggedPitchType[pitcher$TaggedPitchType == "Slider"] = "Cutter"
# for(i in 1:nrow(pitcher)){
#   row=pitcher[i,]
#   if(row$TaggedPitchType=="Curveball"&row$InducedVertBreak>=-5){
#     row$TaggedPitchType="Slider"
#   }
# }
wrong_pitches=c(95,97,99,104,112,165,270)
for(i in wrong_pitches){
   pitcher$TaggedPitchType[pitcher$ID == i] = "Cutter"
}

wrong_pitches <- c(1, 197)

# Remove rows where the ID is in wrong_pitches
pitcher <- pitcher[!(pitcher$ID %in% wrong_pitches),]

wrong_pitches=c(185,194,230)
for(i in wrong_pitches){
   pitcher$TaggedPitchType[pitcher$ID == i] = "Slider"
}

wrong_pitches=c(708,709,716,718,719,722,723,725,727,729,730,732,735,736,741,742,747,755,757,768,771,772,773,774,776,778,779,782,784,785,787,790,795,797,807,812,816,832,835,836,837,840,844,851,858,862,868,870,875,889,897,905,914,923,931,940,943,948,949,953,956,958,959,960,977,990,992,995,1007,1009,1016,1020,1022,1030,1052,1065,1078,1084,1089,1094,1117,1119,1121,1123,1127,1135,1143,135,141,145,152,154,156,164,165,169,172,173,176,178,179,185,186,188,189,198,200,201,210,211,214,229,235,236,254,255,261,265,283,285,288,290,291,294,295,297,303,305,307,310,311,315,317,321,324,327,328,330,334,336,337,341,347,348,349,351,352,353,356,360,361,363,365,368,370,376,377,378,384,386,390,393,397,399,401,402,410,411,420,426,710,711,745,814,919,280,301,302,308,314,316,340,343,344,345,346,359,373,375)
for(i in wrong_pitches){
   pitcher$TaggedPitchType[pitcher$ID == i] = "2-Seam Fastball"
}

wrong_pitches=c(909,932,946,640,693,21,503,296)
for(i in wrong_pitches){
   pitcher$TaggedPitchType[pitcher$ID == i] = "Slider"
}

wrong_pitches=c(888,1033,653,895,655,670)
for(i in wrong_pitches){
   pitcher$TaggedPitchType[pitcher$ID == i] = "Fastball"
}

pitcher$TaggedPitchType[pitcher$ID == 406] = "Slider"
pitcher$TaggedPitchType[pitcher$ID == 77] = "Fastball"
pitcher$TaggedPitchType[pitcher$ID == 309] = "Changeup"
pitcher$TaggedPitchType[pitcher$ID == 85] = "Changeup"
# Uses a for loop to turn specific pitch ID's into different pitches as necessary (pitch ID ovr PitchNo because two different pitches can share a PitchNo)
```

Pitch Charecteristics Chart
```{r, include = FALSE}
# to get the most common tilt
mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}


total_pitches = nrow(pitcher)
scouting_table = pitcher %>%
 filter(!is.na(TaggedPitchType)) %>%
  group_by(TaggedPitchType) %>%
  summarise(NumberPitches = n(),
            UsageRate = paste(round(NumberPitches/total_pitches, 4) * 100, "%"),
            VelocityRange = paste(round(mean(RelSpeed, na.rm = TRUE) - 1), "-" , round(mean(RelSpeed, na.rm = TRUE) + 1)),
            AvgSpinRate = mean(SpinRate, na.rm = TRUE),
            AvgEfficiency=mean(yt_Efficiency),
            AvgTilt=mode(Tilt),
            VAA = mean(VertApprAngle),
            HAA = mean(HorzApprAngle),
            AvgInducedVerticalBreak = mean(InducedVertBreak, na.rm = TRUE),
            AvgHorizontalBreak = mean(HorzBreak, na.rm = TRUE)
            ) %>%
  arrange(desc(NumberPitches))


scouting_table_gt <- scouting_table %>%
  gt() %>%
  tab_header(title = "Pitch Characteristics") %>%
  fmt_number(columns = vars(VelocityRange, AvgSpinRate, AvgEfficiency, AvgTilt, AvgInducedVerticalBreak, AvgHorizontalBreak, HAA, VAA), decimals = 2) %>%
  cols_label(
    TaggedPitchType = "Pitch",
    NumberPitches = "No.",
    UsageRate = "Usage%",
    VelocityRange = "Velocity",
    AvgSpinRate = "Spin",
    AvgInducedVerticalBreak = "IVB",
    AvgHorizontalBreak = "HorzB",
    HAA="HAA",
    VAA="VAA",
    AvgTilt="Tilt",
    AvgEfficiency="Efficiency"
    
  ) %>%
  tab_style(
    style = cell_fill(color = "lightgrey"),
    locations = cells_column_labels(everything())
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything())
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "grey", weight = px(1)),
    locations = cells_body(everything())
  ) %>%
  cols_align(
    align = "center",
    columns = vars(NumberPitches, UsageRate, AvgSpinRate, AvgEfficiency, AvgTilt, AvgInducedVerticalBreak, AvgHorizontalBreak, HAA, VAA)
  ) %>%
  tab_options(
    table.border.top.color = "black",
    table.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.border.top.color = "black",
    table.border.top.width = px(2),
    table.border.bottom.width = px(2)
  ) 
unique_pitches <- unique(scouting_table$TaggedPitchType)
for (pitch in unique_pitches) {
  if (pitch %in% names(pitch_colors)) {
    scouting_table_gt <- scouting_table_gt %>%
      tab_style(
        style = list(
          cell_fill(color = pitch_colors[pitch]),
          cell_text(color = "white")  # Set text color to white
        ),
        locations = cells_body(columns = vars(TaggedPitchType), rows = TaggedPitchType == pitch)
      )
  }
}
```

```{r}
scouting_table_gt
```

Results Chart
```{r}

results_table = pitcher %>%
 filter(!is.na(TaggedPitchType)) %>%
  group_by(TaggedPitchType) %>%
  summarise(NumberPitches = n(),
            WhiffRate = paste(round(sum(PitchCall == "StrikeSwinging" & !is.na(PitchCall)) / sum((!is.na(PitchCall) & PitchCall == "Foul") | (!is.na(PitchCall) & PitchCall == "InPlay") | (PitchCall == "StrikeSwinging" & !is.na(PitchCall))), 3) * 100, "%"), 
            CalledStrikeRate = paste(round(sum(PitchCall == "StrikeCalled" & !is.na(PitchCall)) / sum((!is.na(PitchCall) & PitchCall == "StrikeCalled") | (PitchCall == "BallCalled" & !is.na(PitchCall)) | (PitchCall == "StrikeSwinging" & !is.na(PitchCall))  | (PitchCall == "HitByPitch" & !is.na(PitchCall))), 3) * 100, "%"),
            Balls=mean(PitchCall == "BallCalled") * 100,
            HardHit=mean(ExitSpeed>=95, na.rm = TRUE) *100,
            GB=mean(Angle<=10, na.rm = TRUE)*100,
            FB=mean(Angle>25 & Angle<50, na.rm = TRUE)*100
            ) %>%
  arrange(desc(NumberPitches))

## Make a better table using gt
# Create the gt table and explicitly apply colors
results_table_gt <- results_table %>%
  gt() %>%
  tab_header(title = "Pitch Results") %>%
  fmt_number(columns = vars(WhiffRate, CalledStrikeRate, Balls, HardHit, GB, FB), decimals = 2) %>%
  cols_label(
    TaggedPitchType = "Pitch",
    NumberPitches = "No.",
    WhiffRate = "Whiff%",
    CalledStrikeRate = "Called Strike%",
    Balls="Ball%",
    HardHit="HardHit%",
    GB="Ground Ball%",
    FB="Fly Ball%"
  ) %>%
  tab_style(
    style = cell_fill(color = "lightgrey"),
    locations = cells_column_labels(everything())
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything())
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "grey", weight = px(1)),
    locations = cells_body(everything())
  ) %>%
  cols_align(
    align = "center",
    columns = vars(WhiffRate, CalledStrikeRate, Balls, HardHit, FB, GB)
  ) %>%
  tab_options(
    table.border.top.color = "black",
    table.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.border.top.color = "black",
    table.border.top.width = px(2),
    table.border.bottom.width = px(2)
  ) 
unique_pitches <- unique(results_table$TaggedPitchType)
for (pitch in unique_pitches) {
  if (pitch %in% names(pitch_colors)) {
    results_table_gt <- results_table_gt %>%
      tab_style(
        style = list(
          cell_fill(color = pitch_colors[pitch]),
          cell_text(color = "white")  # Set text color to white
        ),
        locations = cells_body(columns = vars(TaggedPitchType), rows = TaggedPitchType == pitch)
      )
  }
}
```

```{r}
results_table_gt
```

Pitch Movement Plot
```{r}
plot_filtered <- pitcher %>%
  filter(!is.na(HorzBreak) & !is.na(InducedVertBreak))
max_range <- max(abs(plot_filtered$HorzBreak), abs(plot_filtered$InducedVertBreak))

# Create the ggplot
pitch_movement_plot <- ggplot(plot_filtered, aes(x = HorzBreak, y = InducedVertBreak, color = TaggedPitchType)) +
  geom_point(size = 3, alpha = 0.4) +
  geom_hline(yintercept = 0, linewidth = 0.5, color = "black") +
  geom_vline(xintercept = 0, linewidth = 0.5, color = "black") +
  labs(
    title = "Pitch Movement",
    x = "Horizontal Break (in.)",
    y = "Induced Vertical Break (in.)",
    color = "Pitch Type"
  ) +
  scale_color_manual(values = pitch_colors) +
  coord_fixed(ratio = 1, xlim = c(-max_range, max_range), ylim = c(-max_range, max_range)) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
    axis.title = element_text(size = 10),
    legend.title = element_text(size = 15),
    legend.text = element_text(size = 12)
  )
```

```{r, height = 3, width = 3}
pitch_movement_plot
```

Locations Charts
```{r}
pitcher <- pitcher %>%
  mutate(BatterSide = ifelse(BatterSide == "Switch", "Right", BatterSide))

horizontal_limits <- max(abs(c(-1.5, 1.5, min(pitcher$yt_PlateLocSide), max(pitcher$yt_PlateLocSide))))

# Create the ggplot
gLocations = ggplot(pitcher, aes(x = yt_PlateLocSide, y = yt_PlateLocHeight, color = TaggedPitchType)) +
  geom_point(alpha = 0.8, size = 3) +  # Plot the points with some transparency
  ## Draw rectangle and make sure it is in the center
    geom_rect(aes(xmin = -1.5, xmax = 1.5, ymin = .5, ymax = 4), 
            color = "black", fill = NA) +  # Add strike zone rectangle +
  ## Size graph so rectangle is in middle on 
  coord_fixed(xlim = c(-3, 3), ylim = c(0, 5)) +
  scale_color_manual(values = pitch_colors) +  # Apply the custom color palette
  facet_wrap(~BatterSide) +  # Facet by BatterSide
  labs(title = "Pitch Locations from Catcher View",
       x = "Horizontal Location",
       y = "Vertical Location",
       color = "Pitch Type") +
  xlim(-horizontal_limits, horizontal_limits)+
  theme(
    plot.title = element_text(hjust = 0.5, size = 15, face = "bold"),
    axis.title = element_text(size = 10),
    legend.title = element_text(size = 15),
    legend.text = element_text(size = 12)
  )
```

```{r}
gLocations
```

Create Lefty Hitter Situation Chart
```{r}
df_list=list()
for (i in 0:3){
  for (j in 0:2){
    x=pitcher %>% filter(BatterSide=="Left", Balls==i, Strikes==j) %>% 
  group_by(TaggedPitchType) %>%
  summarize(count = n()) %>% mutate(percentage = round((count / sum(count)) * 100, 2), Count=str_glue('{i}-{j}'))
    df_list[[length(df_list) + 1]]=x
  }
}
merged_df <- bind_rows(df_list)

```

```{r}

test=dcast(merged_df,TaggedPitchType~Count, value.var = "percentage")
desired_order <- c(1,2,3,4)  # This example reorders rows 2, 4, 1, 3

# Reorder the data frame based on desired order
test <- test[desired_order, ]
```

```{r}
gt_table <- test %>%
  gt() %>%
  sub_missing(missing_text = 0) %>% 
  tab_header(title = "LHH Pitch Percentages") %>%
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "grey", weight = px(1)),
    locations = cells_body(everything())) %>% 
  tab_options(
    table.border.top.color = "black",
    table.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.border.top.color = "black",
    table.border.top.width = px(2),
    table.border.bottom.width = px(2)
  )
unique_pitches <- unique(results_table$TaggedPitchType)
for (pitch in unique_pitches) {
  if (pitch %in% names(pitch_colors)) {
    gt_table <- gt_table %>%
      tab_style(
        style = list(
          cell_fill(color = pitch_colors[pitch]),
          cell_text(color = "white")  # Set text color to white
        ),
        locations = cells_body(columns = vars(TaggedPitchType), rows = TaggedPitchType == pitch)
      )
  }
}

# Display the table
gt_table
```


Create Righty Hitter Situation Chart (Same Code, but BatterSide=="Right")
```{r}
df_list=list()
for (i in 0:3){
  for (j in 0:2){
    x=pitcher %>% filter(BatterSide=="Right", Balls==i, Strikes==j) %>% 
  group_by(TaggedPitchType) %>%
  summarize(count = n()) %>% mutate(percentage = round((count / sum(count)) * 100, 2), Count=str_glue('{i}-{j}'))
    df_list[[length(df_list) + 1]]=x
  }
}
merged_df <- bind_rows(df_list)

```

```{r}

test=dcast(merged_df,TaggedPitchType~Count, value.var = "percentage")
desired_order <- c(1,2,3,4)  # This example reorders rows 2, 4, 1, 3

# Reorder the data frame based on desired order
test <- test[desired_order, ]
```

```{r}
gt_table <- test %>%
  gt() %>%
  sub_missing(missing_text = 0) %>% 
  tab_header(title = "RHH Pitch Percentages") %>%
  cols_align(
    align = "center",
    columns = everything()
  ) %>%
  tab_style(
    style = cell_borders(sides = "all", color = "grey", weight = px(1)),
    locations = cells_body(everything())) %>% 
  tab_options(
    table.border.top.color = "black",
    table.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.border.top.color = "black",
    table.border.top.width = px(2),
    table.border.bottom.width = px(2)
  ) 
  
unique_pitches <- unique(results_table$TaggedPitchType)
for (pitch in unique_pitches) {
  if (pitch %in% names(pitch_colors)) {
    gt_table <- gt_table %>%
      tab_style(
        style = list(
          cell_fill(color = pitch_colors[pitch]),
          cell_text(color = "white")  # Set text color to white
        ),
        locations = cells_body(columns = vars(TaggedPitchType), rows = TaggedPitchType == pitch)
      )
  }
}

# Display the table
gt_table
```


Situations Table
```{r}
situation = pitcher %>% 
  
  group_by(TaggedPitchType) %>%
  filter(!is.na(TaggedPitchType)) %>%
  summarize(LHH = sum(BatterSide == "Left", na.rm = TRUE),
            RHH = sum(BatterSide == "Right", na.rm = TRUE),
            Ahead = sum(Strikes > Balls),
            Behind = sum(Strikes < Balls & Strikes != 2)
            ) %>% 
  mutate(percentage_lhh = (LHH / sum(LHH)) * 100,
         percentage_rhh = (RHH / sum(RHH)) * 100,
         percentage_ah = (Ahead / sum(Ahead)) * 100,
         percentage_beh = (Behind / sum(Behind)) * 100
         ) %>%
  select(TaggedPitchType, percentage_lhh, percentage_rhh, percentage_ah, percentage_beh) %>%
    arrange(desc(percentage_ah))
  

## Make a gt table with same color palette as above
situation_table = situation %>%
  gt() %>%
  tab_header(title = "Usage Rate by Situation") %>%
  cols_label(
    TaggedPitchType = "Pitch",
    percentage_lhh = "LHH",
    percentage_rhh = "RHH",
    percentage_ah = "Ahead",
    percentage_beh = "Behind"
  ) %>%
  fmt_number(
    columns = vars(percentage_lhh, percentage_rhh, percentage_ah, percentage_beh),
    decimals = 2
  ) %>%
  tab_options(
    table.border.top.color = "black",
    table.border.bottom.color = "black"
  )

for (pitch in unique_pitches) {
  if (pitch %in% names(pitch_colors)) {
    situation_table <- situation_table %>%
      tab_style(
        style = list(
          cell_fill(color = pitch_colors[pitch]),
          cell_text(color = "white")  # Set text color to white
        ),
        locations = cells_body(columns = vars(TaggedPitchType), rows = TaggedPitchType == pitch)
      )
  }
}

```

```{r}
situation_table
```
```{r}
test2=pitcher %>% group_by(TaggedPitchType) %>% summarise("horz"=mean(HorzRelAngle), "vert"=mean(VertRelAngle))
ggplot(test2, aes(x = horz, y = vert, color = TaggedPitchType)) +
  geom_point(size=(12)) +
  labs(title = "Average Release Angles by Pitch Type",
       x = "Horizontal Release Angle",
       y = "Vertical Release Angle") +
  theme_minimal() +
  theme(legend.title = element_text(size = 17, face = "bold"),  # Customize legend title appearance
        legend.text = element_text(size = 15),
        panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank(),
    plot.title = element_text(hjust = 0.75, size=20)) +
  coord_cartesian(xlim = c(-15, 5), ylim = c(-15, 5))
```

```{r}
plot_filtered <- pitcher %>%
  filter(!is.na(HorzBreak) & !is.na(InducedVertBreak))


plot_filtered <- plot_filtered %>%
  mutate(id = row_number())


max_range <- max(abs(plot_filtered$HorzBreak), abs(plot_filtered$InducedVertBreak))


plot(
  plot_filtered$HorzBreak,
  plot_filtered$InducedVertBreak,
  xlab = "Horizontal Break (in.)",
  ylab = "Induced Vertical Break (in.)",
  main = "Pitch Movement",
  col = as.factor(plot_filtered$TaggedPitchType),
  pch = 19,
  xlim = c(-max_range, max_range),
  ylim = c(-max_range, max_range)
)


abline(h = 0, v = 0, col = "black")


selected_points <- identify(
  plot_filtered$HorzBreak,
  plot_filtered$InducedVertBreak,
  labels = plot_filtered$id,
  plot = TRUE
)


selected_points
```

